NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-08 Manuscript/manuscriptPS.tex
Update manuscriptPS.tex

\emph{Numerical simulations of S-DROSS curves.}
The numerical simulations of S-DROSS curves were performed with the SIMPSON simulation package \cite{bak00}
using as input the $^{13}$C--$^1$H
dipolar couplings, either as determined by the R-PDLF experiments, or as calculated from the known $^2$H quadrupolar couplings \cite{browning80}.
The chemical shift anisotropy and homonuclear couplings were neglected, and the input file {\it{rep2000}}\todo{citation needed?} was used to simulate a random
distribution of bilayer orientations in the samples studied.

@@

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data were collected using
the Open Collaboration method \cite{botan15}, with
the NMR\-lipids Project blog (\url{nmrlipids.blogspot.fi}) and
GitHub repository (\url{github.com/NMRlipids/NMRlipidsIVotherHGs})
as the communication platforms.
The simulated systems are listed in 
Tables \ref{PSsystems} (pure PS bilayers without additional ions) 
and \ref{mixedIONsystems} (mixed PC:PS bilayers at various salt concentrations).
Further simulation details are given in the SI.
The simulation data are also indexed in a
searchable database available at \url{www.nmrlipids.fi},
and in the NMRlipids/MATCH repository (\url{github.com/NMRlipids/MATCH}).

The C--H bond order parameters were calculated directly
from the carbon and hydrogen positions using the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C--H bond and the membrane normal
(taken to align with $z$, with bilayer periodic in the $xy$-plane).
Angular brackets denote average over all sampled configurations.
The order parameters were first calculated averaging over time separately
for each lipid in the system. The average and
the standard error of the mean were then calculated over different lipids.
Python program ({\tt scripts/calcOrderParameters.py}) that uses the
MDAnalysis library \cite{agrawal11,gowers16} is available in Ref. \citenum{MATCHgit}. 
The number density profiles were calculated using the {\tt gmx density} tool
of the Gromacs sofware package \cite{gromacsMANUAL}.

>>>>

\emph{Numerical simulations of S-DROSS curves.}
The numerical simulations of S-DROSS curves were performed with the SIMPSON simulation package \cite{bak00}
using as input the $^{13}$C--$^1$H
dipolar couplings, either as determined by the R-PDLF experiments, or as calculated from the known $^2$H quadrupolar couplings \cite{browning80}.
The chemical shift anisotropy and homonuclear couplings were neglected, and the input file {\it{rep2000}} was used to simulate a random
distribution of bilayer orientations in the samples studied.

@@

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data were collected using
the Open Collaboration method \cite{botan15}, with
the NMR\-lipids Project blog (\url{nmrlipids.blogspot.fi}) and
GitHub repository (\url{github.com/NMRlipids/NMRlipidsIVotherHGs})
as the communication platforms.
The simulated systems are listed in 
Tables \ref{PSsystems} (pure PS bilayers without additional ions) 
and \ref{mixedIONsystems} (mixed PC:PS bilayers at various salt concentrations).
Further simulation details are given in the SI, and
the simulation data are indexed in a
searchable database available at \url{www.nmrlipids.fi},
and in the NMRlipids/MATCH repository (\url{github.com/NMRlipids/MATCH}).

The C--H bond order parameters were calculated directly
from the carbon and hydrogen positions using the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C--H bond and the membrane normal
(taken to align with $z$, with bilayer periodic in the $xy$-plane).
Angular brackets denote average over all sampled configurations.
The order parameters were first calculated averaging over time separately
for each lipid in the system. The average and
the standard error of the mean were then calculated over different lipids.
Python program ({\tt scripts/calcOrderParameters.py}) that uses the
MDAnalysis library \cite{agrawal11,gowers16} is available in Ref. \citenum{MATCHgit}. 
The ion \todo{There are ion number densities, right?} number density profiles were calculated using the {\tt gmx density} tool
of the Gromacs sofware package \cite{gromacsMANUAL}.
